Verifying Demonstrations

### 2018-11-30 paper/conclusions.tex

In this paper, we have introduced \CROCUS, a privacy-preserving protocol for verifiably counting participants at protests. 
Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
%To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
%Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \CROCUS fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests. }
%With respect to privacy, \CROCUS provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \CROCUS).
\sonja{update sec analysis results}

>>>>

In this paper, we have introduced \CROCUS, a privacy-preserving protocol for verifiably counting participants at protests. 
Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest, with the following caveat. Given the conflict between verifiability and receipt-freeness when counting presence, any digital trace needed for verifiability could conceivably be used to substantiate a claim that was by itself weaker. For instance if there is auxiliary information that points to a person having participated in a protest, for example pictures at the event, with face recognition and subsequent identification, IP address of the person's home router, etc., then any remaining uncertainty from false positives could be reduced by learning from data on the ledger and the person's smartphone. This potential difference can thus be considered the price for verifiability. Against an attacker without such side information, \CROCUS preserves the participants' privacy, expressed in terms of unlinkability to their identity and between events.

%To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
%Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \CROCUS fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests. }
%With respect to privacy, \CROCUS provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \CROCUS).
\sonja{update sec analysis results}
